\documentclass[margin,line]{res}
\usepackage{multicol, enumitem, url}

\usepackage[backend=biber,
            sorting=none,
            defernumbers=true,
            firstinits=true,
            maxbibnames=99,
            hyperref=true]{biblatex} % load the package
\DeclareNameAlias{author}{last-first}
\renewbibmacro{in:}{} % get rid of "In:"
\addbibresource{../bib/papers.bib}
\addbibresource{../bib/posters.bib}
\addbibresource{../bib/talks.bib} % add a bib-reference file

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue,
}

\urlstyle{same}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\pagestyle{plain} % page numbers
 

\begin{document}
\nocite{*}
\name{Amin Shirazi \hfil\today \vspace*{.1in}}

\begin{resume}

\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
3220, Snedecor Hall &	{\it Phone:}  (515) 708-6372 \\
Iowa State University & {\it E-mail:} ashirazi@iastate.edu\\
2438 Osborn Drive & \url{ashirazist.github.io} \\
Ames, Iowa 50011-1090  & \\


\end{tabular}


\section{\sc Education}
{\bf Iowa State University (ISU)}, Ames, Iowa USA\\
\vspace*{-.1in}
\begin{list1}
\item[]Ph.D Students, Statistics, August 2017 - Present 
\begin{list2}
\vspace*{.05in}
%\item[] Dissertation title:  ``On advancing MCMC-based methods for Markovian data structures with applications to deep learning, simulation, and resampling''
\item[] Advisor: Peng Liu
\end{list2}
\vspace*{.05in}

\end{list1}
{\bf Shahid Beheshti University, Tehran, Iran} \\
{\em Department of Statistics, Faculty of Mathematical Science}\\
\vspace*{-.1in}
\begin{list1}
\item[]M.S., Statistics, February 2014
\begin{list2}
\vspace*{.05in}
\item[] Research title:  ``Testing Statistical Hypothesis for Jump Models in Stochastic Differential Equations''
\item[] Advisors: Hamideh D. Hamedani,  AriReza Taheriyoun
\end{list2}
\vspace*{.05in}
\end{list1}

{\bf Imam Khomeini International University of Qazvin, Qazvin, Iran} \\
{\em 	Department of Statistics, Faculty of Science}\\
\vspace*{-.1in}
\begin{list1}
	\item[]B.S., Statistics, September 2010
	\begin{list2}
		\vspace*{.05in}
		\item[] Research title:  ``Simulation in Statistical Models''
		\item[] Advisor: Afshin Fallah
	\end{list2}
\end{list1}
\section{\sc Research Interests}
\begin{itemize}
	\item Statistical analysis of big data
	\item Applying integrated data analysis on -Omics data using a range of network based and Bayesian based methods
	\item Statistical Genomics
	\item Microbiome data analysis
	\item Statistical data analytics methods for high-dimensional data and pre-clinical studies
	\item Statistical Learning
	\item Computational Statistics
	\item Reproducible Research
\end{itemize}



\section{\sc Publications }
%\printbibliography[keyword=refereed, heading=none, resetnumbers=true]
\begin{enumerate}
		\item \textbf{Amin Shirazi}, Hamideh D. Hamedani, ‘‘Model Selection for Stock Market Using Statistical Hypothesis Testing ", The First FINACT conference of Mathematical Finance and Actuary”, Institute For Research in Fundamental Sciences (IPM), Oral presentation, (August 2014) 
\end{enumerate}
\section{\sc Preprints}	
\begin{enumerate}
		\item  Mohammad Jafari, Fangwei Hou, \textbf{Amin Shirazi}, Mostafa Hassanalian, "Determination of Experimental/Numerical Errors on Identification of Flutter Derivatives for a NACA 0020 Airfoil", \textit{AIAA SciTech Forum and Exposition} (in review)  
\end{enumerate}	
\section{\sc Article in Preparation}
\begin{enumerate}
	\item 	Mohammad Jafari, Fangwei Hou, \textbf{Amin Shirazi}, "Experimental Identification of Aeroelastic Wind Load Parameters with Uncertainty: Design of Experiment Method"
	
	\item Mohammad Jafari, Fangwei Hou, \textbf{Amin Shirazi}, "Sensitivity Analysis of Effective Parameters and Prediction of Across-wind Response of Tall Buildings in Time Domain"
	
	\item \textbf{Amin Shirazi}, Hamideh D. Hamedani, “Can Noise Pollution Be Modeled by Pure Jump Processes?”
	
	\item Ali Sharifi, Hamideh D. Hamedani, \textbf{Amin Shirazi}, “Statistical Hypothesis for Continuous-Time Processes”. 
\end{enumerate}
\section{\sc Research Experience}
{\bf Iowa State University}

{\em Research and Teaching Assistant } \hfill {\bf August 2017- present}


\vspace{-.3cm}
Statistical data analysis of big data and specifically applying integrated data analysis on -Omics data using heterogeneous network based and Bayesian based methods using data analytics approaches.

\vspace{-.3cm}

Working in a multidisciplinary research in  the intersection of statistics and genetics, analytical clinical trials and in general statistical Genomics with a penchant for statistical learning and reproducibility



{\bf Shahid Beheshti University}

{\em Research Assistant } \hfill {\bf March 2014- January 2017}

\vspace{-.3cm}
Research assistant in researches whose aims were  model selection for stock market using statistical hypothesis testing, applying statistical hypothesis to continuous-time processes and modeling pure jump processes. 

\vspace{-0.3cm}

The leader of a research group of 6 graduate and undergraduate students to gather, clean and analyze stock market data. Model selection for stock market data using statistical hypothesis testing   utilizing statistical methods to 100+ stock market data sets using R to evaluate model robustness and diagnosing the models insufficiency.
	




\section{\sc Honors and Awards}

{\em Shahid Beheshti University} \hfill 2014\\
 Ranked $5^{th}$ among all graduate students of mathematical statistics in MS program, Department of Statistics, Faculty of Mathematical Science 
 
{\em Master's Entrance Exam, Iran} \hfill 2011\\
Ranked $17^{th}$ in national master entrance exam among more than 8000 applicants 

{\em Imam Khomeini International University of Qazvin, Qazvin, Iran}\hfill 2010\\
Ranked $5^{th}$ in the whole four-year bachelor study among 41 students in undergraduate program, Department of Statistics, Faculty of Science\\

{\em Semi-finalist in the National Statistics Olympiads, Iran}\hfill 2009


\section{\sc Package Development}


{\em PetFindr}

\vspace{-.3cm}
PetFindr (R package) provides an R interface for the Petfinder.com API (V2). Once a user obtains an API key and secret from Petfinder, this package allows the user to retrieve information about animals by type, breed, location, and other useful characteristics. (\url{https://earl88.github.io/PetFindr/index.html})



\section{\sc Teaching Experience}

{\bf Iowa State University, Ames, Iowa USA}

{\em Instructor} \hfill { Fall 2019}

\vspace{-.3cm}
Course instructor for STAT 305 (Engineering Statistics) (\url{https://ashirazist.github.io/stat305.github.io/index.html}). Statistics for engineering problem solving, covering principles of engineering data collection, descriptive statistics, elementary probability distributions, principles of experimentation, confidence intervals and significance tests, one- and two-sample studies, regression analysis, and statistical software. Approximately 70 students.

{\em Co-Instructor} \hfill { Summer 2019}

\vspace{-.3cm}
Course co-instructor for STAT 305, online section (Engineering Statistics). Statistics for engineering problem solving, covering principles of engineering data collection, descriptive statistics, elementary probability distributions, principles of experimentation, confidence intervals and significance tests, one- and two-sample studies, regression analysis, and statistical software. Approximately 100 students.

{\em Teaching Assistant} \hfill { Spring 2019}

\vspace{-.3cm}
Teaching assistant for STAT 588 (Statistical Theory for Research). Responsible for teaching some parts of the course, helping construct tests, grading assignments, maintaining weekly office hours to communicate in person with students as needed. Approximately 30 students.

{\em Teaching Assistant} \hfill { Fall 2018}

\vspace{-.3cm}
Teaching assistant for STAT 330 (Probability and Statistics for Computer Science). Responsible for  helping construct tests, grading assignments, maintaining weekly office hours to communicate in person with students as needed. Approximately 80 students.

{\em Teaching Assistant} \hfill { Spring 2017}

\vspace{-.3cm}
Teaching assistant for STAT 305  (Engineering Statistics). Responsible for grading assignments, maintaining weekly office hours to communicate in person with students as needed. Approximately 90 students.

{\em Grading Assistant} \hfill { Fall 2017}

\vspace{-.3cm}
Teaching assistant for STAT 305  (Engineering Statistics). Responsible for grading weekly quizzes and assignments. Approximately 70 students.

{\em Grading Assistant} \hfill { Fall 2017}

\vspace{-.3cm}
Teaching assistant for STAT 226  (Introduction to Business Statistics). Responsible for grading assignments and exams with eight other graders to share the grading across all nine sections. Approximately 700 students in all sections.


{\bf Shahid Beheshti University, Tehran, Iran}

{\em Grading Assistant} \hfill { Spring 2013}

\vspace{-.3cm}
Mathematical analysis II. Responsible for grading assignments, scheduling review sessions for exams. 

{\em Teaching Assistant} \hfill { Fall 2012}

\vspace{-.3cm}
Stochastic processes. Responsible for teaching some parts of the course, designing and grading assignments. 

{\bf Imam Khomeini International University of Qazvin, Qazvin, Iran}

{\em Teaching Assistant} \hfill { Fall 2009}

\vspace{-.3cm}
Mathematical Statistics II. Responsible for Giving and grading quizzes, grading homework, solving necessary or requested problems for students. 

{\bf Mahestan Educational Institute, Tehran, Iran}

\vspace{-.3cm}
{\em Instructor} \hfill { September 2011 - April 2012}

\vspace{-.3cm}
Technical Instructor for national master entrance exam applicants. Responsible for statistical consultant and technical instructor, helping applicants with their questions and advising them to choose the most appropriate graduate program related to their interests.


\section{\sc Work \\ Experience}
{\bf Koosha Setareh Iranian International Co, Tehran, Iran}


{\em Data Analyst, R \& D Department} \hfill { July 2015- July 2017}

\vspace{-.3cm}
 Benefited statistical skills to interpret market data in corporation with sales and marketing department, fitted generalized linear model to data from market research, predicting demands for products and services, supervised and accurately predicted demands for products and services,  sales analysis and predicting future trends using data analytical methods,	generated creative business reports, tables, charts, and graphs for the logistic department and management board({\url{http://kooshasetarehpasargad.com/koosha/en/}} )



{\bf Iranian Shaygan Pars, Tehran, Iran }


{\em Data Analyst, R \& D Department} \hfill {  September 2014- June 2015}

\vspace{-.3cm}
Interpreted sales data applying statistical models as a teamwork with sales department,	presented results to senior managers and regulatory authorities, predicted demands for products and services, collected data to monitor levels of progress in sales and customer satisfaction


{\bf Info Tech International Company, Tehran, Iran }

{\em Data Analyst, R\&D Department\\ 
	 R\&D Consultant of PSP (Payment Service Provider) Department
} \hfill {  May 2014- September 2014}

\vspace{-.3cm}
Designed opinion polls to collect and analyze data using SAS, programmed software codes to identify trends and relationships within the data utilizing R, conducted tests for big data validation using statistical knowledge and analytical methods, design of experiment methods in optimization, call center consultant for designing, collecting and analysis of customer satisfaction survey 
({\url{http://infotech-co.com/}})


{\bf Mahestan Educational Institute, Tehran, Iran }

{\em Director Consultant and Technical Instructor} \hfill {  September 2011- April 2012 }

\vspace{-.3cm}
{\em Educational board}\\
Instructor of statistical core courses, approximately 100 undergraduate students, student consultant 
 



\section{\sc Service and Leadership}

{\bf Iowa State University}


{\em Statistics in the Community (StatCom) Executive Committee} \hfill {August 2019- present}

\vspace{-0.3cm}
{\em STATCOM at Iowa State offers statistical advice and expertise free of charge to governmental and nonprofit groups in the local community.
	
\vspace{-0.3cm}
Currently working on a project with Ames Public Library to conduct and analyze a survey on their services to library members}

\vspace{-0.3cm}
{\em Statistics faculty committee - student representative	} \hfill {August 2019- present }

\vspace{-0.3cm}
Communicate relevant information from the student association to the faculty members, provide students’ feedback of the departmental decisions 

{\em STATers - social committee } \hfill {August 2017 - present}

\vspace{-0.3cm}
social organization for graduate students

{\em Iranian Students and Scholars' Association, treasurer} \hfill {Fall 2018- Fall 2019}

\vspace{-0.3cm}
Event planner for 5 big events for the members of the association and non-Iranian people, organized the new year celebration event and hosted approximately 300 people, communicated with finance committee and senate of Iowa State University for funds to hold events




\section{\sc Professional Affiliations}
American Statistical Association (ASA), Institute of Mathematical Statistics (IMS)\\
Iranian Statistical Society(ISS)


\section{\sc Computing}
\begin{list2}
\newcommand{\latex}{\LaTeX\xspace}	
\item Mathematical and Statistical Computing:  R, SAS; some experience with HTML;\\
 Currently learning  SQL, Spark and Scala.
\item Reporting:  \LaTeX, Markdown, HTML, Shiny
\item Content Management: Git



\end{list2}

%\clearpage





%\begin{list2}
%\item StatCom, community service organization
%\begin{itemize}
%\item[--] Executive Committee, 2013 - 2017
%\item[--] Network Outreach Coordinator, 2015 - 2017
%\end{itemize}
%\item ISU Department of Statistics, Student Representative to Faculty Meetings, 2015 - 2017
%\item STATers, social organization for graduate students, Vice President, 2013 - 2014
%\item Graduate and Professional Student Senate, Senator, 2012 - 2013
%\end{list2}




\clearpage
%\section{\sc Relevant Coursework}
%\begin{multicols}{2}
%\begin{list2}
%\item Bayesian Statistics*
%\item Theory of Probability and Statistics I \& II*
%\item Statistical Methods I \& II*
%\item Introduction to Statistical Computing*
%\item Mathematical Statistics I \& II*
%\item Theory of Probability*
%\item Applied Bayesian Analysis*
%\item Methods of Correlation and Regression*
%\item Integral Transforms*
%\item Methods of Real Analysis*
%\item Probability I
%\item Real Analysis I
%\item Linear Algebra and Matrix Theory
%\item Introduction to Mathematical Modeling
%\item Scientific Computation in Numerical Analysis
%\item Methods of Applied Mathematics
%\item Algebraic Structures I \& II
%\item Theory of Functions of Complex Variables
%\item Introduction to Number Theory
%\item Partial Differential Equations and Applications
%\item Differential Equations
%\item Vector Calculus
%\item Error-Correcting Codes
%\item Logic, Sets, and Functions
%\item Elements of Computers \& Programming
%\item Elements of Software Design
%\end{list2}
%\end{multicols}
%
%\vspace{-.5cm}
%* Denotes graduate level coursework.



\end{resume}
\end{document}
